%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% This fork/modified version has been made by Nicolás Omar González Passerino (nicolas.passerino@gmail.com, 15 Oct 2020)
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}


\geometry{left=1cm,right=1cm,top=1cm,bottom=1cm,columnsep=0.75cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}
\usepackage{blindtext}
\usepackage{multicol}
\usepackage{soul} % for custom underlining


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
% If using xelatex or lualatex:
\setmainfont{Roboto Slab}
\setsansfont{Lato}
\renewcommand{\familydefault}{\sfdefault}
\else
% If using pdflatex:
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
% \usepackage{sourcesanspro}
\renewcommand{\familydefault}{\sfdefault}
\fi

%Famous Colors
\definecolor{GitHubColor}{HTML}{171515}
\definecolor{YouTubeColor}{HTML}{b2071d}
\definecolor{LinkedInColor}{HTML}{0e76a8}
\definecolor{KotlinPurpleColor}{HTML}{B125EA}
\definecolor{KotlinPurbleBlueColor}{HTML}{7F52FF}
\definecolor{KotlinRoseColor}{HTML}{E24462}
\definecolor{AndroidGreenColor}{HTML}{689F38}
\definecolor{SwiftOrangeColor}{HTML}{f05039}
\definecolor{iOSBlueColor}{HTML}{007AFF}


% Another Colorful and Creative Palette
%PINK
%\definecolor{PrimaryColor}{HTML}{E13F79}    % Main text and headings (Pink)
%\definecolor{SecondaryColor}{HTML}{5B7FC5}  % Subheadings and accents (Light Pink)
%\definecolor{TertiaryColor}{HTML}{5B7FC5}   % Highlight or accent color (Light Blue)
%\definecolor{QuaternaryColor}{HTML}{ACD68B} % Alternative accent color (Pale Green)
%\definecolor{BackgroundColor}{HTML}{F5F5F5}  % Background color (Light Gray)

% Eye-Appealing Color Palette
\definecolor{PrimaryColor}{HTML}{2C3E50}  % Main text and headings (Deep Blue-Gray)
\definecolor{SecondaryColor}{HTML}{3D3B40}  % Subheadings and accents (Charcoal Gray)
\definecolor{TertiaryColor}{HTML}{2A3D45}   % Highlight or accent color (Dark Steel Blue)
\definecolor{QuaternaryColor}{HTML}{1E4258} % Alternative accent color (Dark Teal Blue)
\definecolor{BackgroundColor}{HTML}{F8F8F8} % Background color (Soft Light Gray)



\colorlet{name}{PrimaryColor}
\colorlet{tagline}{PrimaryColor}
\colorlet{heading}{PrimaryColor}
\colorlet{headingrule}{PrimaryColor}
\colorlet{subheading}{SecondaryColor}
\colorlet{accent}{TertiaryColor}
\colorlet{emphasis}{SecondaryColor}
\colorlet{body}{SecondaryColor}

\pagecolor{BackgroundColor}


% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small\bfseries}
\renewcommand{\cvsectionfont}{\large\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
%% \addbibresource{sample.bib}
% \documentclass[12pt]{scrartcl}
\usepackage{lipsum}
\usepackage{wasysym}
%\usepackage{lstdoc}
%
%
\usetikzlibrary{calc}
%

\setlength\multicolsep{0pt}

\begin{document}

\name{Mohamed Almahdy}
\tagline{Mobile Applications Developer}
\personalinfo{
\email{engmohamedalmahdy@gmail.com}\smallskip
\mobile{+201096475710}
\location{Nasr City, Cairo}
\youtube{LightFeather42}
\linkedin{https://www.linkedin.com/in/eng-mohamed-almahdy}
\github{https://github.com/eng-mohamedalmahdy}
}

\makecvheader


% ----- ABOUT ME -----


\cvsection{Profile}
\begin{quote}

\textbf{Mobile Apps Engineer} with \textbf{5 years} of experience in Kotlin, Java, and Swift.
Successfully created \textbf{10+ Apps} in \textbf{Android, iOS, and KMP}, improving app stability by \textbf{40\%} and performance by \textbf{30\%}.
Enhanced engagement by \textbf{25\%} and reduced API response time by \textbf{50\%}.
Skilled in product thinking, identifying critical business opportunities and enhancing product strategy.



\end{quote}


% ----- ABOUT ME -----

% ----- EXPERIENCE -----
\cvsection{Experience}

\cvevent{Mobile Application Developer}{| \href{https://www.linkedin.com/company/tawuniya/}{\textbf{Tawuniya}}}{11/2024 -- Now}{Riydah, KSA (Remote)}
\begin{itemize}
\item Developing the \href{https://play.google.com/store/apps/details?id=za.co.vitalitydrive.tawuniya}{\textbf{Tawuniya Drive App}}, a mobility and insurance companion app enhancing driving safety through telematics and real-time user engagement features.
\item Collaborated on the \textbf{Tawuniya Drive SDK}, a Kotlin Multiplatform (KMP) SDK encapsulating domain \& data layers to ensure consistency, scalability, and developer productivity across shared modules.
\item Working on migrating native applications to \textbf{Flutter}, bridging native platform SDKs via \textbf{Method Channels} and applying \textbf{BLoC} state management with \textbf{Clean Architecture}.
\end{itemize}
\divider

\cvevent{Mobile Application Developer}{| \href{https://www.linkedin.com/company/thekupe-consultancy/}{\textbf{The Kupe Consultancy}}}{03/2024 -- 11/2024}{Remote}
\begin{itemize}
\item Fully developed 2 KMP production apps: \hyperlink{ion}{\textbf{Ion Community}} (residential community platform, MVI + Compose Multiplatform) and \textbf{Ures} (real estate CRM for lead \& property management), applying \textbf{Clean Architecture} and \textbf{Ktor Client}.
\end{itemize}
\divider

\cvevent{Mid-Level Android Developer}{| \href{https://www.linkedin.com/company/dtag/}{\textbf{DTag}}}{07/2022 -- 03/2024}{Cairo, Egypt}
\begin{itemize}
\item Contributed to 2 mobile apps:
\begin{itemize}
\item \hyperlink{whizzy}{\textbf{Whizzy}} (iOS) Mobile app designed to simplify the process of renting vehicles for short rides.
\item \hyperlink{samoolah}{\textbf{Samoolah}} (Android) Services provider app with dual distributions: customer-facing app and technician/driver app.
\end{itemize}
\end{itemize}
\divider



\cvevent{Junior Software/Android Developer}{| \href{https://www.linkedin.com/company/virtualworkernow/}{\textbf{Virtual Worker Now}} \& \href{https://www.linkedin.com/company/elmnassa/}{\textbf{ElMnassa Innovation}}}{07/2021 -- 07/2022}{Cairo, Egypt}
\begin{itemize}
\item Contributed to multiple mobile apps including \hyperlink{pet_materices}{\textbf{Pet Matrices}} (iOS) and the \href{https://virtualcoursesnow.com/vcn-home/}{\textbf{VirtualCoursesNow}} website.
\end{itemize}


% ----- EXPERIENCE -----


\columnratio{0.33}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.



\begin{paracol}{2}

% ----- LEARNING -----

\cvsection{Languages}
\cvtag{Kotlin}
\cvtag{Java}
\cvtag{Swift}
\cvtag{Dart}

\cvsection{Frameworks}
\cvtag{Android}
\cvtag{KMP}
\cvtag{iOS}
\cvtag{Flutter}

\cvsection{Android Tools}
\cvtag{Compose}
\cvtag{Coroutines}
\cvtag{Retrofit}
\cvtag{Koin \& Hilt}
\cvtag{WorkManager}
\cvtag{Room}


\cvsection{IOS Tools}
\cvtag{SwiftUI}
\cvtag{UIKit}
\cvtag{Core Data}
\cvtag{Combine}

\cvsection{Flutter Tools}
\cvtag{BLoC}
\cvtag{Method Channels}

\switchcolumn


% ----- EDUCATION -----
\cvsection{Education}
\cvevent{B.S. in Computer Engineering | \textbf{Al-Azhar University}}{\hfill\faCalendar 2017--2021}{}
\normalsize\begin{itemize}
\item Graduation Project: \textbf{Zakerly ( E-learning Mobile App )} Grade : \textbf{Excellent}
\end{itemize}
% ----- EDUCATION -----


\cvsection{SKILLS \& EXPERTISE}
{\normalsize\begin{itemize}

\item \textbf{Software Architecture}: Expert in \textbf{MVVM, Clean Architecture}, \& \textbf{SOLID}.
\item \textbf{Async Programming}: Coroutines, GCD, and Rx for concurrency.
\item \textbf{Design Patterns}: Applying proven patterns for scalable Apps.
\item \textbf{Cross-Platform Development}: Kotlin Multiplatform and Flutter for shared logic \& UI.
\item \textbf{Networking \& API Design}: REST, WebSockets, GraphQL, and caching.
\item \textbf{Database \& Persistence}: Room, Core Data, and advanced caching.
\item \textbf{Dependency Injection}: Expertise in Dagger Hilt, Koin \& DI concepts
\item \textbf{Testing \& CI/CD}: Unit tests, UI tests, and automated pipelines.
\item \textbf{Declarative UI}: Jetpack Compose, Compose Multiplatform, and SwiftUI.
\item \textbf{State Management}: MVI, BLoC, and MVVM for reactive, predictable UI.
\item \textbf{SDK \& Modular Arch}: Building KMP SDKs and feature-based modular apps.

\end{itemize}}


%% ----- Books -----
%\cvsection{Recent Books Readings}
%\begin{multicols}{3}
%
%{\small\begin{itemize}
%\item[\textcolor{PrimaryColor}{\faBook}] Clean Mobile Arch.
%\item[\textcolor{PrimaryColor}{\faBook}] Clean Arch.
%\item[\textcolor{PrimaryColor}{\faBook}] Gradle for Android
%\item[\textcolor{PrimaryColor}{\faBook}] Head First OOA/D
%\item[\textcolor{PrimaryColor}{\faBook}] Algos Unplugged
%\item[\textcolor{PrimaryColor}{\faTrello}] \href{https://trello.com/b/pkZlgQVu/my-readings-board}{My book list: \textbf{\textcolor{TertiaryColor}{HERE}}}
%\end{itemize}}
%\end{multicols}

% ----- Books -----
\end{paracol}

\cvsection{Projects}
\vspace{2px}

\cvsubsection{\color{AndroidGreenColor}\faAndroid Android Projects}
\vspace{2px}




\cvevent{\color{AndroidGreenColor}}{\cvrepo{\color{AndroidGreenColor}\underline{\textbf{Tawuniya Drive}|\faGooglePlay\faAndroid}}{https://play.google.com/store/apps/details?id=za.co.vitalitydrive.tawuniya}}{}{}
\begin{itemize}
\item A mobility and insurance companion app designed to enhance driving safety and user experience.
\item \textbf{Tech Stack}: Jetpack Compose, Hilt, Coroutines, Kotlinx Serialization, Retrofit
\item \textbf{CI/CD}: Configured automated build and deployment pipelines using Codemagic
\end{itemize}
\divider


\hypertarget{samoolah}{}
\cvevent{}{\cvrepo{\color{AndroidGreenColor}\underline{\textbf{Samoolah}|\faLock\faAndroid}}{https://play.google.com/store/apps/details?id=com.dtag.samoolah.customer}}{}{}
\begin{itemize}
\item Services provider app with dual distributions: customer-facing app for booking services and technician app for service fulfillment.
\item \textbf{Tech Stack}: MVVM, Modularization, Jetpack Compose, Retrofit, Navigation Component, Kotlin Coroutines \& Flows
\end{itemize}
\divider


\cvevent{}{\cvrepo{\color{AndroidGreenColor}\underline{\textbf{Grainoz}|\faAndroid\faGithub}}{https://github.com/eng-mohamedalmahdy/grainoz-android}}{}{}
\begin{itemize}
\item Pet needs delivery e-commerce platform serving multiple user roles with feature-based modular architecture and Clean Architecture principles.
\item \textbf{Tech Stack}: Jetpack Compose, MVVM, Koin DI, Ktor Client, Kotlin Multiplatform modules, Arrow-kt, Paging 3, Coil 3
\end{itemize}
\divider



\vspace{6px}
\cvsubsection{\color{SwiftOrangeColor}\faApple iOS Projects}
\vspace{2px}


\hypertarget{whizzy}{}
\cvevent{}{\cvrepo{\color{SwiftOrangeColor}\underline{\textbf{Whizzy}|\faApple}}{https://github.com/eng-mohamedalmahdy/Whizzy-overview}}{}{}
\begin{itemize}
\item Vehicle rental mobile app designed to simplify the process of renting vehicles for short rides with seamless booking experience.
\item \textbf{Tech Stack}: SwiftUI, MVVM, Alamofire, Kingfisher, Combine \& GCD
\end{itemize}
\divider



\hypertarget{pet_materices}{}
\cvevent{\color{SwiftOrangeColor}\textbf{Pet Matrices}}{\cvrepo{\color{SwiftOrangeColor}|\faLock\faApple}{}}{}{}
\begin{itemize}
\item Pet lifestyle application for tracking pet activities, calorie intake, health conditions, and receiving expert veterinary advice.
\item \textbf{Tech Stack}: SwiftUI, MVVM, REST API, Swift GCD
\end{itemize}
\divider



\vspace{6px}
\cvsubsection{\color{KotlinPurbleBlueColor}\kotlinicon Kotlin Multiplatform Projects}
\vspace{2px}

\cvevent{}{\cvrepo{\color{KotlinPurbleBlueColor}\underline{\textbf{HappyTail}|\kotlinicon \faGithub}}{}}{}{}
\begin{itemize}
\item Veterinary clinic and pet care platform with dual applications: customer app for booking services and shopping, plus driver app for service delivery.
\item Built with Kotlin Multiplatform (KMP) for seamless cross-platform development across Android \& iOS.
\item \textbf{Tech Stack}: MVVM, Compose Multiplatform, Koin DI, Ktor, Navigation Compose, KotlinX Serialization, Coil 3, Moyasar Payment SDK, MapLibre Maps, Moko Resources
\end{itemize}
\divider


\hypertarget{ion}{}
\cvevent{\color{KotlinPurbleBlueColor}\href{https://play.google.com/store/apps/details?id=com.thekupe.ion_community}{\textbf{Ion Community}}| \kotlinicon }{}{}{}
\begin{itemize}
\item Residential compound community app showcasing developer projects, events, and compound amenities for residents.
\item Built with Kotlin Multiplatform (KMP) for seamless cross-platform development across Android \& iOS.
\item \textbf{Tech Stack}: MVI, Compose Multiplatform, Ktor, Voyager Navigation, KotlinX Serialization, KAMEL
\end{itemize}
\divider
%hyperlink

\hypertarget{ures}{}

\cvevent{\color{KotlinPurbleBlueColor}\textbf{Ures}| \kotlinicon }{}{}{}
\begin{itemize}
\item Real estate CRM companion app designed to help sales agents and brokers manage leads, properties, and client interactions efficiently.
\item \textbf{Tech Stack}: MVI, Compose Multiplatform, Ktor, KotlinX Serialization, Coil
\end{itemize}
\divider

\begin{center}
\textbf{\Large \href{https://github.com/eng-mohamedalmahdy}{More Projects at my GitHub}}
{\cvrepo{\color{GitHubColor}\faGithub}
{https://github.com/eng-mohamedalmahdy}}{}{}
\end{center}
\divider

\end{document}
